Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-05-29 paper/main.tex
folded back in a bit of the gluing stuff to make things concrete

The locality and gluing axioms \cite{bakerMathsSheaf} of a sheaf describe the conditions for verifying that the sections over subspaces are part of a cohesive section over the whole space. The locality axiom asserts that two sections in a sheaf are equal when they evaluate to the same values over the same set of open sets. The gluing axiom asserts that the union of sections defined on specific open sets is equivalent to one big section over the union of spaces. The gluing axiom therefore expresses an equivalency between a concatenated representation of data and the distributed representation of the same data. In \autoref{fig:atct:networkbundle} this axiom means that the sections over each node and the edge can be combined into one section over the piece of the network in the figure.

>>>>

The locality and gluing axioms \cite{bakerMathsSheaf} of a sheaf describe the conditions for verifying that the sections over subspaces are part of a cohesive section over the whole space. The locality axiom asserts that two sections in a sheaf are equal $\dsection^{a} = \dsection^{b}$ when they evaluate to the same values over the same set of open sets $\desection^{a}|{\openset} =  \dsection^{b}|_{openset}$. The gluing axiom asserts that the union of sections defined on specific open sets is equivalent to one big section over the union of spaces $\dsection|_{\openset_{i} \sqcup \openset_{j}} = \dsection^{i}|_{\openset_i} \sqcup \dsection^{j}|_{\openset_j}$ if these sections agree on overlaps $\dsection^{i}|_{\openset_i\cap\openset_j} =  \dsection^{j}|_{\openset_i\cap\openset_j}$ The gluing axiom generalizes to expresses an equivalency between a concatenated representation of data and distributed representation of the same data. In \autoref{fig:atct:networkbundle} this axiom means that the sections over each node and the edge can be combined into one section over the piece of the network in the figure.
